Visualizing the CTMC and SAOM fitting process

### 2017-01-23 VisualizingSAOMsOutline.Rmd
ideas for ch 1

>>>>

# Ideas from "Visualizing Statistical Models: Removing the Blindfold"

1. Introduction
    a. Talk about the toolbox of visualizations. We must answer the question, "What is in the network visualization toolbox?" and use those tools and more moving forward.
2. Background 
    a. Model family - the SAOM is the model family
    b. Model form - which $\beta$ effects get included
    c. Fitted model - estimates of rate parameters and $\beta$s resulting from `RSiena` fit
    d. Question: Can we find a direct interpretation of the SAOM $\beta$ parameters? 
    e. Question: How can we visualize these networks interactively?? 
3. Display the Model in Data-Space
    a. What does visualizing the model in the data space mean for SAOMs? 
        i. Idea: take the `sims` output object from the SAOM model fit. Create adjaceny matrices from them, tile them in `geom_tile`, shading by frequency of specific ties in simulations, then overlay the squares that are in the data that was being simulated. 
        ii. Idea: focus on the probabilities of individual tie changes. How do close probabilities affect overall model behavior?? 
4. Collections are more informative than singletons
    a. We've already done some of this - densities of fitted estimates from `RSiena`. 
    b. Look at distributions of fitted network statistics (corresponding to stats in model form) by the fitted parameter values. I also think we've already done some of this. 
    c. Other ideas????
5. Do not just look at the final result; explore how the algorithm works
    a. Idea: We've already discussed visualizing the microsteps from current time to the next time point.
    b. Idea: Look at the chains for updating the parameter estimates -- use multiple starting values.
